\gettitle

### 2019-12-01 assignment3/submission3.tex
Correct solutions to Exercise 1

\begin{figure}[ht!]
\begin{tikzpicture}[scale=0.15]
\foreach \x in {1,...,97} {
	\draw (\x,0) -- (\x, 2);
	\draw (\x, -5) -- (\x, -7);
};
\draw (0,0) -- (97,0);
\draw (0,-5) -- (97,-5);
\node at(0, -1) {\tiny Master};
\node at(0, -4) {\tiny Slave};
\foreach \x/\n in {3/7,9/8,15/9,21/10,27/11,33/12,39/13,45/14,51/15,57/16,63/17,69/18,75/19,81/20,87/21,93/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,1) (a\n) {}
		node[below=7mm, above of=a\n] {\tiny \n};
};
\foreach \x/\n in {3/3,9/4,15/5,21/6,27/7,33/8,37/9,41/10,45/11,49/12,53/13,57/14,61/15,65/16,69/17,73/18,77/19,81/20,87/21,93/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,-6) (b\n) {}
		node[above=7mm, below of=b\n] {\tiny \n};
};
\path[draw,->] 
	(b5.north) edge (a10.south)
	(a11.south) edge (b8.north);
\end{tikzpicture}
\caption{Solution for Figure 1}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((10 - 5) - (8 - 11)) = \frac12(5 + 3) = 4  &\\
d = 1 & \\
\Delta = 12, C_s(t_4 + \Delta) = 20 & \\
\frac{dC_S}{dt} = \frac{12 + 4}{12} = \frac{4}{3} &
\end{align*}

\begin{figure}[ht!]
	\begin{tikzpicture}[scale=0.15]
	\foreach \x in {1,...,97} {
		\draw (\x,0) -- (\x, 2);
		\draw (\x, -5) -- (\x, -7);
	};
	\draw (0,0) -- (97,0);
	\draw (0,-5) -- (97,-5);
	\node at(0, -1) {\tiny Master};
	\node at(0, -4) {\tiny Slave};
	\foreach \x/\n in {3/1,9/2,15/3,21/4,27/5,33/6,39/7,45/8,51/9,57/10,63/11,69/12,75/13,81/14,87/15,93/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,1) (a\n) {}
			node[below=7mm, above of=a\n] {\tiny \n};
	};
	\foreach \x/\n in {3/6,9/7,15/8,21/9,27/10,33/11,49/12,65/13,81/14,87/15,93/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=3mm] at(\x + .5,-6) (b\n) {}
			node[above=7mm, below of=b\n] {\tiny \n};
	};
	\path[draw,->]
		(b8.north) edge (a4.south)
		(a5.south) edge (b11.north);
\end{tikzpicture}
\caption{Solution for Figure 2}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((4 - 8) - (11 - 5)) = \frac12(-4 - 6) = -5  &\\
d = 1 & \\
\Delta = 3, C_s(t_4 + \Delta) = 14 & \\
\frac{dC_S}{dt} = \frac{3}{3 +5} = \frac{3}{8} &
\end{align*}

>>>>

\begin{figure}[ht!]
\begin{tikzpicture}[scale=0.2]
\foreach \x in {1,...,81} {
	\draw (\x,0) -- (\x, 2);
	\draw (\x, -5) -- (\x, -7);
};
\draw (0,0) -- (81,0);
\draw (0,-5) -- (81,-5);
\node at(0, -1) {\tiny Master};
\node at(0, -4) {\tiny Slave};
\foreach \x/\n in {3/7,8/8,13/9,18/10,23/11,28/12,33/13,38/14,43/15,48/16,53/17,58/18,63/19,68/20,73/21,78/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,1) (a\n) {}
		node[below=7mm, above of=a\n] {\tiny \n};
};
\foreach \x/\n in {3/3,8/4,13/5,18/6,23/7,28/8,31/9,34/10,37/11,40/12,43/13,46/14,49/15,52/16,55/17,58/18,63/19,68/20,73/21,78/22} {
	\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,-6) (b\n) {}
		node[above=7mm, below of=b\n] {\tiny \n};
};
\path[draw,->] 
	(b5.north) edge (a10.south)
	(a11.south) edge (b8.north);
\end{tikzpicture}
\caption{Solution for Figure 1}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((10 - 5) - (8 - 11)) = \frac12(5 + 3) = 4 &\\
d = 1 & \\
\Delta = 6, C_s(t_4 + \Delta) = 18 & \\
\frac{dC_S}{dt} = \frac{6 + 4}{6} = \frac{5}{3} &
\end{align*}

\begin{figure}[ht!]
	\begin{tikzpicture}[scale=0.2]
	\foreach \x in {1,...,81} {
		\draw (\x,0) -- (\x, 2);
		\draw (\x, -5) -- (\x, -7);
	};
	\draw (0,0) -- (81,0);
	\draw (0,-5) -- (81,-5);
	\node at(0, -1) {\tiny Master};
	\node at(0, -4) {\tiny Slave};
	\foreach \x/\n in {3/1,8/2,13/3,18/4,23/5,28/6,33/7,38/8,43/9,48/10,53/11,58/12,63/13,68/14,73/15,78/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,1) (a\n) {}
			node[below=7mm, above of=a\n] {\tiny \n};
	};
	\foreach \x/\n in {3/6,8/7,13/8,18/9,23/10,28/11,41/12,55/13,68/14,73/15,78/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,-6) (b\n) {}
			node[above=7mm, below of=b\n] {\tiny \n};
	};
	\path[draw,->]
		(b8.north) edge (a4.south)
		(a5.south) edge (b11.north);
\end{tikzpicture}
\caption{Solution for Figure 2}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((4 - 8) - (11 - 5)) = \frac12(-4 - 6) = -5  &\\
d = 1 & \\
\Delta = 3, C_s(t_4 + \Delta) = 14 & \\
\frac{dC_S}{dt} = \frac{3}{3 +5} = \frac{3}{8} &
\end{align*}
